Manuscript

### 2021-01-18 Manuscript/Manuscript.Rmd
separate Results code into different chunks and complete paragraph

```{r Setup, include=FALSE, cache.vars='annotation_summary'}

@@

first_query_file <- file.path("Annotations", "Records_2020-12-11", "Records_11.12.20.xlsx")

@@

The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review. Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.

Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is used then to reclassify all records (P tasks).

>>>>

```{r Setup, include=FALSE}

@@

@@

```{r Result 1}

first_batch <- "Records_2020-12-11"

first_query_file <- file.path("Annotations", first_batch, "Records_11.12.20.xlsx")

new_uncertains <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_uncertain') %>% pull(Value) %>% sum

new_positives <- annotation_summary %>% filter(Batch == first_batch & Label == 'New_positive') %>% pull(Value) %>% sum

task_table <- summary_table[[1]]$`Task type` %>% table
```

The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
Of these records, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review. Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_positive, percent(Reviewed_positive/Reviewed)))` were labeled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed_negative, percent(Reviewed_negative/Reviewed)))` as negative.

Subsequently, cycles of prediction/review tasks were performed, in which manually reviewed records (R tasks) were used to train the ML classification algorithm which is used then to reclassify all records (P tasks). In total `r task_table[['R']] - 1` review tasks were required in addition to the initial one (tab. 1), for a total of `r sum(new_uncertains, new_positives)` extra reviewed articles (`r new_uncertains` predicted as uncertain and `r new_positives` as positive). After task 11, the two susbsequent P tasks returned no uncertain or positive prediction which were not already reviewed and therefore the first cycle was termined.
